Scale Space Edge Detection

### 2018-03-06 paper.tex
what is all this crap
yup
fix this pllzzzkzz

\begin{equation}
  I_n(x) = i^{-\alpha}J_{\alpha}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+\alpha+1)}\left(\frac{x}{2}\right)^{2m+\alpha}
\end{equation}

@@

\section{Defining an Edge in Scale Space}
We classify edge points as points which have gradient magnitueds that assume a maximum in the direction of the gradient. Let us denote the magnitude of the gradient of $L$ as $L_g$. Then we define an edge in the scale space with the following conditions

\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{gg} &= 0 \\
    L_{ggg} &< 0
  \end{aligned}
\end{equation}

@@

\begin{equation}
  \begin{aligned}
    L_{gg} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{ggg} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}

@@

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{Images/lena.jpg}
  \caption{Original Grayscale Lena Image}
  \label{lena_o}
\end{figure}

@@

\begin{equation}
  \begin{aligned}
    [D_y] &=
    \begin{bmatrix}
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.046548 &-0.122572  &0.0  &0.122572  &0.046548 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776
    \end{bmatrix} \\
    [D_x] &= [D_y]^T
  \end{aligned}
\end{equation}

@@

\newpage

@@

@@

\lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}

>>>>

\begin{equation}
  I_n(x) = i^{-n}J_{n}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+n+1)}\left(\frac{x}{2}\right)^{2m+n}
\end{equation}

@@

\section{Defining an Edge in Scale Space}
We classify edge points as points which have gradient magnitude that assume a maximum in the direction of the gradient. Let us denote the magnitude of the gradient of $L$ as $L_v$. Then we define an edge in the scale space with the following conditions

\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}

@@

\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}

@@

The first scale derivative of the gradient magnitude is calculated as follows

\begin{equation}
  \partial_t (G_{\gamma}L) = \gamma t^{\gamma-1}(L_x^2+L_y^2) + t^{\gamma}(L_x(L_{xxx}+L_{yyy})+L_y(L_{xxy} + L_{yyy}))
\end{equation}

Then the second scale derivative of the gradient magnitude is

\begin{equation}
  \begin{align}
  \partial_{tt} &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
   &+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
   &+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2 \\
   &+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
   &+L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
  \end{align}
\end{equation}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{Images/lena/lena_orig.png}
  \caption{Original Lena Image}
  \label{lena_o}
\end{figure}

@@

\begin{equation}
  \begin{aligned}
    [D_x] &=
    \begin{bmatrix}
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.046548 &-0.122572  &0.0  &0.122572  &0.046548 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776
    \end{bmatrix} \\
    [D_y] &= [D_x]^T
  \end{aligned}
\end{equation}

@@

@@

With these calculations we now can check all the conditions necessary to define an edge in scale space.

@@

% \lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}
